---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
https://chat.qwen.ai/c/cfabef59-277a-4c4c-8348-4c9eb68e1baa 
# 激活 r43 环境
conda activate bioR43

# 安装 IRkernel（R 的 Jupyter 支持）
R -e "install.packages('IRkernel', repos='https://cran.rstudio.com/')"

# 注册为 Jupyter Kernel（显示名称为 "R 4.3"）
R -e "IRkernel::installspec(name = 'bioR43', displayname = 'bioR43')"

方法 A：通过 Notebook 选择 Kernel
打开 .ipynb 文件。
点击右上角的 Kernel 名称（如 “Python 3.10”）。
在列表中选择：
“R 4.3”
“R 4.4”
点击 “Select”。
方法 B：通过命令面板选择
按 Ctrl+Shift+P（Windows/Linux）或 Cmd+Shift+P（macOS）。
输入：

通过 Conda 环境启动 VS Code。
解决：在终端中激活 Conda 环境后启动 VS Code：
bash

conda activate bioR43
code .        # 打开 VS Code 并进入当前目录

Jupyter: Select Interpreter to Start Jupyter Server 

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
