---
title: "Demon Of RMarkdown"
author: "Zhen Gao"
date: "2025-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Mutation Annotation Format (MAF) 
This package attempts to summarize, analyze, annotate and visualize MAF files any studies in MAF format, including TCGA 
maftools functions can be categorized into mainly Visualization and Analysis modules.

Install from Bioconductor repository 


```{r libarary}
# Install from GitHub repository
# BiocManager::install("PoisonAlien/maftools")
# BiocManager::install("maftools")
# install.packages("mclust")

```

# Ctrl k, then ctrl s  --> select the cmd  for cetain issue 
# Ctrl + Alt + I   ask AI
# Ctrl + Alt + D  delete the line 
# Ctrl + Alt + X  delete the right space
# Ctrl + Shift + X  显示扩展菜单
# Ctrl + /   comment the line 
# Ctrl + Del  delete a world 


# Ctrl +  
# Ctrl +  
# Ctrl +  


```{r cars}
library(maftools)
```



```{r pressure, echo=FALSE}
# path to TCGA LAML MAF file
# AML as the abbreviation for acute myeloid leukemia
# LAML used within TCGA for unkown reason 
# https://gdc.cancer.gov/resources-tcga-users/tcga-code-tables/tcga-study-abbreviations

laml.maf = system.file('extdata', 'tcga_laml.maf.gz', package = 'maftools') 

#clinical information containing survival information and histology. This is optional
laml.clin = system.file('extdata', 'tcga_laml_annot.tsv', package = 'maftools') 

laml = read.maf(maf = laml.maf, clinicalData = laml.clin)

laml

```

2 space in the end of line means change line 

General Markdown Formatting (for both HTML and PDF where supported):
Bold: **bold text** or __bold text__  
Italic: *italic text* or _italic text_  
Italic bold: *__italic text__* or _**italic text**_  
Strikethrough: ~~strikethrough~~  
Code: `` code ``  
Superscript: text^super^  
Subscript: text~sub~  


<span style="color: red;">This text is red.</span>  
<span style="color: blue;">This text is blue.</span>  
<span style="color: orange;">This text is blue.</span>  
<span style="color: purple">This text is blue.</span>  
<span style="color: lightgray">This text is blue.</span>  
<span style="color: lightblue">This text is blue.</span>  
<span style="color: limon">This text is blue.</span>  
<span style="color: cyan">This text is blue.</span>  
<span style="color: magenta">This text is blue.</span>  
<span style="color: olive">This text is blue.</span>  
<span style="color: pink">This text is blue.</span>  

<span style="color: #FF5733;">This text uses a hexadecimal color code.</span> 


foo <font color='brown'>bar</font> foo


<a >blue color</a>

	`red color`

#### list 

ordered: 

1. Main item one
    1. Sub-item one
    1. Sub-item two
2. Main item two
    1. Another sub-item


unordered 1:

* Item 1
* Item 2
  * Nested Item 2.1
  * Nested Item 2.2


unordered 2:

+ Item 3
+ Item 4
+ Item 4

unordered 1:

- Item 3
- Item 4
- Item 4
